openarchaeoCollaboration

### 2021-02-06 analysis/paper.Rmd
Start analysis of GitHub API data

>>>>

```{r dependencies, include=FALSE}
library("tidyverse")
library("openarchaeoCollaboration")
```

## Materials and methods

We used *open-archaeo* <https://open-archaeo.info/>, a list of open source archaeological software and other digital resources.
The criteria for inclusion in open-archaeo are [...].
The search strategy for compiling it was [...].

```{r data-oarch}
oarch <- read_csv("https://raw.githubusercontent.com/zackbatist/open-archaeo/master/open-archaeo.csv")
```

We augmented this with data from the GitHub API for records with an associated GitHub repository.

```{r data-github}
oarch %>% 
  mutate(
    gh_repo = str_remove(github, "https://github.com/"),
    gh_repo = str_remove(gh_repo, "/$")
  ) %>% 
  separate(gh_repo, c("gh_owner", "gh_repo"), "/", extra = "drop") %>% 
  mutate(
    gh_lang = ght("GET /repos/{owner}/{repo}/languages", 
                  owner = gh_owner, repo = gh_repo)
  ) ->
  oarch
```

## Results

What languages are people using?

```{r plot-gh_lang}
oarch$gh_lang %>% 
  pivot_longer(everything(), names_to = "language", values_to = "n") %>% 
  drop_na(n) %>% 
  group_by(language) %>% 
  summarise(n = sum(n), .groups = "drop") %>% 
  arrange(-n) %>% 
  slice(1:10) %>% 
  ggplot(aes(fct_reorder(language, n, .desc = TRUE), n)) +
  geom_col() +
  labs(title = "Languages used in GitHub repositories",
       caption = "Data: <https://open-archaeo.info> and the GitHub API",
       x = "Language", y = "Bytes of code")
```
